On Math

### 2025-08-27 cards/paper.tex
limits in trigonometry functions
upload bunch of topics for future redaction

\section{Trigonometry}

@@

@@

The \textbf{Euler characteristic} of any polyhedra is denoted by the
Greek letter $\aleph$ (``k-eye'') and is equal to the number:
\begin{equation}
  \aleph = V - E + F
\end{equation}
Any convex polyhedron has
\begin{equation}
  \aleph = 2
\end{equation}
\section{Vectors}
How to call that section?
\section{Displacement}
\begin{equation}
  s = ut+\frac{1}{2}gt^2
\end{equation}
where:

@@

@@

\subsection{Integral of a reciprocal function}
\begin{equation}
  \int \frac{1}{x} \, dx = \int \ln abs(x) + C
\end{equation}
and also:
\begin{equation}
  \int \frac{1}{x} \, dx = \int \ln|x| + C = \ln abs(x) + \ln K = \ln (K (abs(x))
\end{equation}

@@

>>>>

\section{Trigonometry}
-- TODO: properties of a trigonometric functions
-- like limits, asymptotes etc
\subsection{Properties of a sine function}
zeros of the function
x=n PI
maxima
x = pi/2 + 2npi
minima
x = -pi/2 + 2npi

sine function is odd (which means it has a rotational symmetry around the origin)
sin(-x) = -sin(x)

\subsection{Properties of a cosine function}
\subsection{Properties of a tangent function}
\subsection{Properties of a cosecant function}
y = cscx = 1/sinx
asymptotes: x = n pi
takes a value of 1 at x = pi/2 2npi
takes a value of -1 at x = -pi/2 + 2npi
cosecant is an odd function
\subsection{Properties of a secant function}
y = secx = 1/cosx
asymptotes: x = +- pi/2, +- 3pi/2 etc
takes a value of 1 at x = 2npi
takes a value of -1 at x = pi + 2npi
\subsection{Properties of a cotangent function}
y = cotx = 1 /tanx = cosx/sinx
for zeros x = pi/2 + pi n
vertical asymptotes x = pi n
period pi
cotx is an odd function

\subsection{Pythagorean identity}
\begin{equation}
  \cos^2(\theta) + \sin^2(\theta) = 1
\end{equation}

@@

\subsection{Limits in trigonometric functions}
% TODO: image needed
For sine function:
\begin{equation}
  \lim\limits_{x \to a}\sin x = \sin a \\
  \text{and}
  \lim\limits_{x \to \pm\infty}\sin x = DNE
\end{equation}

Similarily for cosine function:
\begin{equation}
  \lim\limits_{x \to a}\cos x = \cos a \\
  \text{and}
  \lim\limits_{x \to \pm\infty}\cos x = DNE
\end{equation}

Differently for tangens though:
\begin{equation}
  \lim\limits_{x \to a}\tan x = \tan a, a \neq \frac{\pi}{2} + n\pi \\
  \text{because there function does not exist! but they are infinite at the sides of a vertical asymptote:} \\
  \lim\limits_{x \to \frac{\pi}{2}^-}\tan x = \infty \\
  \lim\limits_{x \to \frac{\pi}{2}^+}\tan x = -\infty
\end{equation}

\subsection{Double angle formula for sine}
%TODO
sin(x+y) = sinx cosy + cosx siny
substituting x = y
sin2x = 2sinx cosx
it has many applications, it allows to simplyifying some trigonometric expressions
and find the exact value for some non-special angles
this is an identity! not equation, meaning it's true for all xes
\subsection{Double angle formula for cosine}
%TODO

@@

The \textbf{Euler characteristic} of any polyhedra is denoted by the
Greek letter $\aleph$ (``k-eye'') and is equal to the number:
\begin{equation}
  \aleph = V - E + F
\end{equation}
Any convex polyhedron has
\begin{equation}
  \aleph = 2
\end{equation}
\section{Vectors}
How to call that section?
\subsection{Dot product}
for vectors a, b and c and scalar lambda

- the dot product distributes over addition:
(a+b) * c = a*c + b*c
and
c*(a+b) = a*c + b*c

- the dot product is associative with respect to scalar multiplication
(La) * b = L(a*b)
and
a*(Lb) = L(a*b)

- the dot product is commutative
a*b = b*a

- two non-zero vectors a and b are perpendicular if the angle between them is $\theta = 90$
a perpendicular symbol b

in generat the dot product of two perpendicular vectors is 0. if a perpendicular b and theta is 90 then
a*b = |a| * |b| * cos90 = |a| * |b| * 0 = 9

if a and b are non-zero vectors you can do a conversion
a perp b <=> a*b = 0

\section{Displacement}
\begin{equation}
  s = ut+\frac{1}{2}gt^2
\end{equation}
where:

@@

\subsection{Continuity over an interval}
In general it is said that function $f(x)$ is continuous over the interval $[a, b]$ if it is:

- continuous on the open interval $(a, b)$

- right continuous at $x = a$

- left continuous at $x = b$

\section{Probability}
\subsection{Independent events}
In probability, we say that two events are \textbf{independent} when the outcome of one
event doesn't influence the outcome of the other event. Otherwise, the events are \textbf{dependent}.

As for multiplication law for independent events:
\begin{equation}
  P(A \cap B) = P(A) * P(B)
\end{equation}
but, if A and B are independent, then the probability of B occuring is not influenced by
whether or not A has occured, so:
\begin{equation}
  P(B|A) = P(B)
\end{equation}
and replacing it for the first law it goes:
\begin{equation}
  P(A \cap B) = P(A) * P(B)
\end{equation}

\subsection{The addition law of probability}
\begin{equation}
  P(A \cup B) = P(A) + P(B) - P(A \cap B)
\end{equation}
There's some ince intuition behind this law: by adding $P(A)$ to $P(B)$, we count $P(A \cap B)$ twice, hence we need to get rid of one.

\subsection{The multiplication law for conditional probability}
\begin{equation}
  P(A|B) = \frac{P(A \cap B)}{P(B)}
\end{equation}
% TODO provide an example
\subsection{The law of total probability}
% TODO

\section{Series and Sequences}
It is important to understand the difference between a sequence and a series.
A sequence is a list of numbers (separated by commmas).
A series is what you get when you add all of the terms of a sequence together.
\subsection{The sum of an arithmetic series}
\begin{equation}
  S_N = \sum^N_{n=1}a_n
\end{equation}
alternatively
\begin{equation}
  S_N = \frac{N}{2}(a_1 + a_N)\
end{equation}
also, if you don't know the last element of a series, you can use the following:
\begin{equation}
  S_N = \frac{N}{2}(a_1 + a_N) = \frac{N}{2}(2a_1 + d(N-1))
\end{equation}

@@

\subsection{Integral of a reciprocal function}
\begin{equation}
  \int \frac{1}{x} \, dx = \int \ln abs(x) + C
\end{equation}
and also:
\begin{equation}
  \int \frac{1}{x} \, dx = \int \ln|x| + C = \ln abs(x) + \ln K = \ln (K (abs(x))
\end{equation}
% TODO
more accurate I guess:
\begin{equation}
  \int \frac{1}{ax+b} \, dx = \frac{1}{a} \ln|ax+b| + C
\end{equation}

@@

\subsection{Left Riemann sum}
- underestimates the actual area under the curve, if the function is increasing

- overestimates, if the function is decreasing

\subsection{Implicit differentiation}
%TODO is it a good place?

\subsection{Integrating with substitution}
%TODO example \int 8(2x+5)^3dx
general formula
\begin{equation}
  \int(ax+b)^n dx = \frac{1}{a(n+1)}(ax+b)^{n+1} + C, n \neq -1
\end{equation}
